High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-28 paper/main.tex
added some notes
checking in results writeup for fig 2

>>>>

To evaluate the relation between informativeness and compression for brain
activity from each experimental condition, we trained a series of
across-participant temporal decoders on compressed representations of the data.
Figure~\ref{fig:inflection}A displays the decoding accuracy as a function of
the number of principal components used to represent the data. Several patterns
were revealed by the analysis. First, in general (i.e., across experimental
conditions), decoding accuracy improves as the number of components increases.
However, decoding accuracy peaked at a higher level for experimental conditions
that exposed participants to cognitively richer stimuli. The peak decoding
accuracy was highest for the ``intact'' condition (versus paragraph: $t(XXX) =
XXX, p = XXX$; versus word: $t(XXX) = XXX, p = XXX$; versus rest: $t(XXX) =
XXX, p = XXX$), next highest for the ``paragraph'' condition (versus word:
$t(XXX) = XXX, p = XXX$; versus rest: $t(XXX) = XXX, p = XXX$), and next
highest for the ``word'' condition (versus rest: $t(XXX) = XXX, p = XXX$). 
This ordering implies that cognitively richer conditions evoke more stable brain
activity patterns across people.

The cognitively richer conditions also displayed steeper initial slopes. For
example, the intact condition decoders reached an arbitrarily chosen threshold
of 5\% accuracy using fewer components than the paragraph condition decoders
($t(XXX) = XXX, p = XXX$) or word condition decoders ($t(XXX) = XXX, p = XXX$),
and decoding accuracy never exceeded 5\% for the rest condition. This suggests
that brain activity patterns evoked by cognitively richer conditions are more
compressible, such that representing the data using the same number of
principal components provides more information to the temporal decoders
(Fig.~\ref{fig:inflection}B).

In every experimental condition, decoding accuracy appeared to asymptote (i.e.,
hit an upper limit) beyond some characteristic number of components that
differed across conditions. To quantify the ``inflection points'' at which the
decoding curves in Figure~\ref{fig:inflection}A flattened out, we fit a sigmoid
function to the average decoding curve for each condition. We defined the
inflection point for each condition as the point on the fitted sigmoid where
the second derivative was both positive and less than a threshold value of
0.0001 (i.e., approaching 0 from the right). These inflection points reflect a
``balance'' between higher decoding accuracy (which tends to be better when
more components are used) and compression (which is better for fewer
components). Plotting each condition's inflection point
(Fig.~\ref{fig:inflection}D) reveals that both the number of components and the
decoding accuracy at each inflection point increase systematically across
conditions in proportion to cognitive richness.
